### 2019-06-11 doc/chapters/introduction.tex
changed some lines

Bitcoin-S is a large project found on GitHub implementing many functionalities.
In this work two of them is going to be examined and worked on, namely the \nameref{property_1} and the \nameref{property_2} describer shortly.
Thus, we go through the relevant code parts to verify those properties, look at some challenges with Stainless and see why we should write software with verification in mind.
We will rewrite the code to Pure Scala, because Bitcoin-S is not written in it.

@@

@@

>>>>

Bitcoin-S is a large project found on GitHub implementing many functionalities.
In this work we look at two of them, namely the \nameref{property_1} and the \nameref{property_2} described shortly.
Thus, we go through the relevant code parts to verify those properties, look at some challenges with Stainless and see why we should write software with verification in mind.
We will rewrite the code to Pure Scala, because Bitcoin-S is not written in it.

@@

The decision to verify this property was inspired by the bug found in Bitcoin Core in September 2018  \cite{cve201817144} which allowed to spend the same unspent transaction output (UTXO) in a transaction multiple times.
Hence, new coins could be created out of the air.
Thus, we try to verify the property, that a non-coinbase transaction cannot generate new coins.
Lets name it the \nameref{property_1}.

As we can see later in chapter \ref{chap:verify_check}, we must rewrite a huge part of the code implementing this property.
This reimplementation into Pure Scala needs a lot of time.
So, we adjust the plan and verify another functionality of Bitcoin-S.
Nevertheless, during the analysis of the \nameref{property_1} we look at a bug in Bitcoin-S found during this work and see the code changes for the bugfix in section \ref{sec:bugfix}.

@@

In Bitcoin-S there is a class Satoshis representing an amount of bitcoins.
We look at the verification of the addition of Satoshis with zero Satoshis.
This operation should result in the same amount of Satoshis.
Lets call it the \nameref{property_2}.

Using Stainless, we see the successfull verification of this property.
But the process of the verification with the tool requires many changes in the code, so that Stainless can accept it.
We look at all needed modifications in chapter \ref{chap:verify_add}.
